\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-16 chapters/supplementary.tex
Add comparison details to suppl.

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory and does not scale up well. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} update rule with empirical $\mathcal{O}(N \log N)$ complexity.

@@

\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}
\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive scalar attributes representing split tendencies. On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
\begin{align}
E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
\end{align}

@@

\subsection{CREMI challenge and compared methods}

\subsection{Noise exps}

\begin{itemize}
% \item Equivalence Mutex Watershed and Greedy Edge Contraction
% \item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
\item Noise: also mention details about plots (fix some long-range edges, fix noise seed and vary K)
\item exp. setup details: enforcing local merges, MWS distinguish between repulsive-long, post-processing of small segments, loss, architecture, training parameters, offset patterns
\item 
\end{itemize}

@@

\subsection{Cityscapes exps}
Mention the main trick in the loss: ignore background pixels (so focus on boundaries). Same mapping defined in \ref{eq:mappings}

>>>>

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory and does not scale up well. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity.

@@

\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}
\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies. On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
\begin{align}
E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
\end{align}

@@

\subsection{CREMI challenge and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network.

\paragraph{THRESH and WSDT} The basic post-processing methods we consider cannot take long-range affinities into account, so we only consider direct neighbors affinities and generate a boundary map by taking an average over the 3 directions. Based on this boundary map, we run connected components (THRESH) and we also introduce seeds at the maxima of the smoothed distance transform (WSDT). For WSDT, the degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation. Due to the anisotropy of the data, we generate 2D WSDT superpixels by considering each 2D image in the stack singularly.

\paragraph{Multi-step pipelines} Given the 2D WSDT superpixels, we build a 3D region-adjacency graph such that each node represents a superpixel. The weights of the edges connecting neighboring superpixels are computed by taking an average over both short- and long-range affinities connecting the two regions. We then convert the edge probabilities to signed weights using the logarithmic mapping defined in Eq. \ref{eq:mappings} and solve the multicut problem on this graph. For our experiments, we use the approximate Kernighan-Lin solver \cite{keuper2015efficient,kernighan1970efficient} (MC). In some cases, the long-range affinities predicted by the CNN can connect two superpixels that are not direct-neighbors. Thus, in these cases we introduce additional \emph{lifted} edges in the graph and an instance of the lifted multicut problem (LMC). This time, similarly to the methods mentioned in \cite{beier2016efficient}, we used a combination of approximate solvers consisting in GAEC and Kernighan-Lin. and      Other state-of-the-art multi-step-pipelines for neuron-segmentation first find 2D superpixels using WSDT and then apply a graph partitioning algorithm: in our comparison, we include one pipeline using agglomerative HC with average linkage (avgHC) and one using an approximation of the Lifted Multicut Problem (LMC) \cite{beier2016efficient}.

 \paragraph{Scaling up \algname{} to the full CREMI dataset} Describe all tricks and then present extended Table

\subsection{Use of gradient noise on the CNN predictions} \label{sec:appendix_noise_gen}

\begin{itemize}
% \item Equivalence Mutex Watershed and Greedy Edge Contraction
% \item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
\item Noise: also mention details about plots (fix some long-range edges, fix noise seed and vary K)
\item exp. setup details: enforcing local merges, MWS distinguish between repulsive-long, post-processing of small segments
\item 
\end{itemize}

@@

\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
Mention the main trick in the loss: ignore background pixels (so focus on boundaries). Same mapping defined in \ref{eq:mappings}
